Discrete Quantum Theories and Computing

### 2019-04-04 dissertation.tex
dissertation.lyx "6.1 Summary" Updating...

\section{Conclusion}

Before what we can do further based on this thesis, let's summarize
what we have done previously. In Chapter~\ref{chap:Conventional-Quantum-Theory},
we reviewed what was established in CQT. In particular, Sec.~\ref{CQC1qubitBloch.sec}
studied the geometrical structure of quantum states to prepare replacing
the conventional Hilbert space~$\mathComplex^{D}$ or projective
Hilbert space~$\CP{D-1}$ by its discrete analog in Chapter~\ref{chap:Unrestricted-Finite-Fields}
and~\ref{chap:DQT=000026DQC}. Since the replaced state spaces are
discrete, the quantum computation model could be built upon them naturally.
In Chapter~\ref{chap:Unrestricted-Finite-Fields}, the field of complex
numbers~$\mathComplex$ is replaced by unrestricted finite fields~$\Fq$,
and a valid pure state can be represented as any non-zero vector in
$\Fq^{D}$ and a measure scheme could be defined which only predicts
whether an measurement result is possible or not. \todo{Keep writing\ldots}

>>>>

\section{Summary}

Since conventional quantum theory is defined over the continuum of
complex numbers which cannot be identified with unbounded resources,
it is natural to explore alternative versions of quantum theory incorporate
our limitation of distinguishability. Examining the computational
and physical consequences of such frameworks can yield new insights
into the power and capacity of quantum computing. We have described
two types of discrete quantum theories: quantum theories and computing
over finite fields and quantum interval-valued probability measures.

The theories over finite fields starting with unrestricted discrete
fields (modal theories), then advancing to a more reasonable framework
based on complexifiable discrete fields (discrete quantum theory I),
which not only supports unnaturally efficient deterministic quantum
algorithms but also lacks the ability to .

\todo{Clean up until here\ldots}

....

Before discussing the further extension, let's summarize what we have
done previously. In Chapter~\ref{chap:Conventional-Quantum-Theory},
we reviewed what was established in CQT. In particular, Sec.~\ref{CQC1qubitBloch.sec}
studied the geometrical structure of quantum states to prepare replacing
the conventional Hilbert space~$\mathComplex^{D}$ or projective
Hilbert space~$\CP{D-1}$ by its discrete analog in Chapter~\ref{chap:Unrestricted-Finite-Fields}
and~\ref{chap:DQT=000026DQC}. In Chapter~\ref{chap:Unrestricted-Finite-Fields},
the field of complex numbers~$\mathComplex$ is replaced by unrestricted
finite fields~$\Fq$. Although this modal theory is

, and a valid pure state can be represented as any non-zero vector
in $\Fq^{D}$ and a measure scheme could be defined which only predicts
whether an measurement result is possible or not. \todo{Keep writing\ldots}
